---
title: "Livestock project -preliminary analysis-"
author: "Shun Hasegawa"
date: "03/05/2017"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(dplyr)
library(car)
library(ggplot2)
library(tidyr)
library(ggmap)
library(pander)
load("../Output/Data/all_image.RData")

```

## Introduction
Here, I show the preliminary analysis of rainfall patterns for the livestock project. Firstly, I picked up 13 focal sites which had average annul precipitation = 800 mm ± 20% from SA, VIC and NSW as below.

```{r site_map, echo=FALSE, fig.width=6, fig.height=5, fig.cap="Location of analysed sites."}
mapPoints
```



```{r ann_rain_tbl, echo=FALSE, results='asis'}
set.alignment(c("right", rep("center", 3)))
pander(ann_smmry, caption = "Avg. annual precipitation of the focal sites over the past 100 years with standard deviation (std.).")
```

Then, I assessed extreme dry events in each site for winter, spring and winter & spring (W_S). The extreme events were identified as years with seasonal precipitation falling into less than **5%** quantile of the overall distribution of seasonal precipitation over the past 100 years. 

```{r rain_dist_fig, echo=FALSE, fig.width=6, fig.height=4, fig.cap="Seasonal rain distribution. Years that experienced extreme evets falls less than 5% quantile, shown with red."}
p_rain
```

## Characterisation of rainfall patters in extreme years
I characterized the rainfall pattern during extremely dry years using indices below.

* Avg. wet day rain (Rd)
* Max daily rain
* No. of dry days
* No. of wet days
* Max no. of contiguous duration of dry days
* Max no. of contiguous duration of wet days
* No. of days of each rain class
    + class0 (Rd < 1 mm)
    + class1 (1 < Rd $\leq$ 5 mm)
    + class2 (5 < Rd $\leq$ 20 mm)
    + class3 (Rd > 20 mm)

Below, I summarize multi-sites data and demonstrate the magnitude of extreme events given as $(x_e-x_a)/x_a$, where $x_e$ and $x_a$ are average values in extreme years and across all years, respectively.

```{r mag_extreme_tbl, echo=FALSE, results='asis'}
set.alignment(c("right", rep("center", 3)))
mult_site_smmry_ed <- mult_site_smmry
names(mult_site_smmry_ed) <- gsub("m_", "m\n", names(mult_site_smmry_ed))
pander(mult_site_smmry_ed, split.cells = c(30, rep(10, 4)))
```


Overall, during extremely dry years, rainfall decreased by 68, 75 and 64% in winter, spring and winter & spring, respectively. This may have been driven by extended periods of continuous dry days and a lack of large rainfall (class2 and class3 rain). Below, I demonstrate the distribution of each index and where extreme events fall.


### Wet day rain
```{r wetday_rain_fig, echo=FALSE, fig.width=6, fig.height=4}
p_wetday_rain
```


### Max daily rain
```{r max_rain_fig, echo=FALSE, fig.width=6, fig.height=4}
p_max_rain
```


### No. of dry days
```{r no_drydays_fig, echo=FALSE, fig.width=6, fig.height=4}
p_n_dryday
```

### No. of wet days
```{r no_wetdays_fig, echo=FALSE, fig.width=6, fig.height=4}
p_n_wetday
```


### Max no. of contiguous duration of dry days
```{r no_contig_dry_fig, echo=FALSE, fig.width=6, fig.height=4}
p_n_contig_dry
```


### Max no. of contiguous duration of wet days
```{r no_contig_wet_fig, echo=FALSE, fig.width=6, fig.height=4}
p_n_contig_wet
```


### No. of days of each rain class
```{r rainclass_fig, echo=FALSE, fig.width=6, fig.height=7}
p_rainclass
```

## Summay of focal sites
The indices above are summarised in a table for each site as below. 

```{r site_tbl, echo=FALSE, results='asis'}
l <- dlply(ann_rain_800_season_tbl, .(Site.name),  function(x){
  site <- unique(x[, 1])
  print(site)
  d <- x[, -1]
  set.alignment("right")
  names(d) <- gsub("_", "\n", names(d))
  pander(d, split.cells = c(15, rep(5, 7)), caption = site)
})

l[[1]]
l[[2]]
l[[3]]
l[[4]]
l[[5]]
l[[6]]
l[[7]]
l[[8]]
l[[9]]
l[[10]]
l[[11]]
l[[12]]
l[[13]]

```


